Determining the alternatives for scalar implicature

### 2016-01-27 Paper/Paper.Rmd
got xtable working, should modify? more than one table?

```{r, libraries}
library(ggplot2)
library(knitr)
library(rjson)
library(dplyr)
library(tidyr)
library(gridExtra)
library(jsonlite)
library(png)
library(grid)
# library(langcog)
```

@@

```{r performancePlots, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items. Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b. The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b."}
# Tuned model run data
plotData <- allModelRunData %>%
  mutate(study = ifelse(numAlts == 5, "Full", 
                        ifelse(numAlts == 4, "Top_two", "Entailment"))) %>%
  gather(Experiment, cors, c(corE6, corE11)) %>%
  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))

@@

modifiedPlotData <- plotData %>%
  gather(pragStudy, pragChoice, c(9,11))
fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
      data=subset(modifiedPlotData, study == "Full")) +
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = preds), lty = 4)
fullRepresentationFit
# gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
```

>>>>

```{r, libraries}
library(ggplot2)
library(knitr)
library(rjson)
library(dplyr)
library(tidyr)
library(gridExtra)
library(jsonlite)
library(png)
library(grid)
library(xtable)
# library(langcog)
```

@@

```{r xtable, results = "asis", fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items. Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b. The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b."}
# Tuned model run data
plotData <- allModelRunData %>%
  mutate(study = ifelse(numAlts == 5, "Full", 
                        ifelse(numAlts == 4, "Top_two", "Entailment"))) %>%
  gather(Experiment, cors, c(corE6, corE11)) %>%
  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))

tableCors <- plotData  %>%
  select(cors, study, Experiment) %>%
  unique() %>%
  mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
  spread(Experiment, cors)

names(tableCors) <- c("r", "model", "Experiment")
tableCors <- tableCors[c(1, 3, 2),]
tab <- xtable(tableCors)
print(tab, type="latex")

@@

modifiedPlotData <- plotData %>%
  gather(pragStudy, pragChoice, c(9,11))
fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
      data=subset(modifiedPlotData, study == "Full")) +
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = preds), lty = 4)
# fullRepresentationFit
# gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
```

### 2016-01-27 Paper/Paper.tex
got xtable working, should modify? more than one table?

{\centering \includegraphics{figs/performancePlots-1}

\caption[The left panel shows improved model fit as scale representations are enriched with more scalar items]{The left panel shows improved model fit as scale representations are enriched with more scalar items. Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b. The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b.}\label{fig:performancePlots}
\end{figure*}
\end{CodeChunk}

>>>>

\% latex table generated in R 3.2.3 by xtable 1.8-0 package \% Tue Jan
26 20:47:20 2016

\begin{table}[ht]
\centering
\begin{tabular}{rlrr}
  \hline
 & r & model & Experiment \\ 
  \hline
1 & Entailment & 0.54 & 0.57 \\ 
  3 & Top\_two & 0.84 & 0.90 \\ 
  2 & Full & 0.86 & 0.90 \\ 
   \hline
\end{tabular}
\end{table}
